SBML L3 paper response to reviewers

### 2020-01-24 main.tex
Fix typo spotted by Karthik

Included below is a point-by-point explanation of our responses to the reviewer's comments; in addition, we have also included a separate document showing the detailed differences (generated with the help of latexdiff) between the manuscript of July 2019 and the new version.  The differences include additional minor corrections and updates beyond the changes made for reviewer feedback, which we have done in an effort to improve the manuscript further (for example, by reducing the overall number of citations and improving overall text cohesion).

To the extent possible, we have endeavored to address all of the issues.  We hope that the reviewer's concerns have been addressed adequately and that the manuscript is now ready for publication.

>>>>

Included below is a point-by-point explanation of our responses to the reviewers' comments; in addition, we have also included a separate document showing the detailed differences (generated with the help of latexdiff) between the manuscript of July 2019 and the new version.  The differences include additional minor corrections and updates beyond the changes made for reviewer feedback, which we have done in an effort to improve the manuscript further (for example, by reducing the overall number of citations and improving overall text cohesion).

To the extent possible, we have endeavored to address all of the issues.  We hope that the reviewers' concerns have been addressed adequately and that the manuscript is now ready for publication.
